Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-10-19 Documents/cover_letter.tex
Minor changes for Nature.

    \opening{Dear Editorial Board of Science,}

    Please find enclosed our manuscript ``Effectiveness of UNAIDS
    targets and HIV vaccination across 127 countries,'' which we are
    submitting to Science as a Report.

@@

    This is the first modeling analysis to evaluate the 95–95–95
    UNAIDS target as well as the first assessment of the global impact
    of potential HIV vaccination programs. Our results show that,
    relative to maintaining status quo rates of diagnosis and
    treatment, cumulative global HIV incidence in 2035 would be 54\%
    and 67\% lower upon meeting the 90–90–90 and 95–95–95 targets,
    respectively. The addition of a 50\%-efficacy vaccine in 2020
    gradually scaled up to 70\% coverage, could achieve a further 26\%
    reduction by 2035 beyond the 95–95–95 target alone.

@@

>>>>

    \opening{Dear Editorial Board of Nature,}

    Please find enclosed our manuscript ``Effectiveness of UNAIDS
    targets and HIV vaccination across 127 countries,'' which we are
    submitting to \textit{Nature} as a Letter.

@@

    This is the first modeling analysis to evaluate the 95–95–95
    UNAIDS target as well as the first broad-scale assessment of the
    global impact of potential HIV vaccination programs. Our results
    show that, relative to maintaining status quo rates of diagnosis
    and treatment, cumulative global HIV incidence in 2035 would be
    54\% and 67\% lower upon meeting the 90–90–90 and 95–95–95
    targets, respectively. The addition of a 50\%-efficacy vaccine in
    2020 gradually scaled up to 70\% coverage, could achieve a further
    26\% reduction by 2035 beyond the 95–95–95 target alone.

@@

    We believe our letter will be approximately 4 pages when
    formatted.
